Leadership across cultures and contexts: an exploratory analysis

### 2020-05-15 leadership_across_cultures_contexts.Rmd
Got shamans into upset plot. Updated caption.

```{r fivefold, fig.width=10, fig.cap="The intersections of evidence for our five basic dimensions of leadership among all text records (an 'upset' plot) [@gehlenborg2019]."}
upset(df_fivefold2, order.by = 'freq', point.size = 5, text.scale = 2, nintersects = 18)
```

As Figure \@ref(fig:fivefold) reveals, descriptions of leadership in the ethnographic record includes a heterogeneous mix of these traits. In particular, not all leaders have evidence for high *Social capital*, leaders with *Cognitive capital* provide benefits *and* impose costs, and *Somatic capital* is rarely mentioned, but when it is, it is associated with providing benefits as well as imposing costs.

<!-- Leadership and followership stem from biological market forces and information-processing roles [e.g., @garfield_evolutionary_2019; @hagen_leadership_2019; @pietraszewski_evolution_2019]. Much of human leadership goes beyond group coordination problems, such as leaders important roles in devising strategic outcomes between individuals, offering advice or decision-making services to individuals, and in making direct prosocial investments that do not involve substantial coordination. We therefore suggest leadership dynamics emerge from inter-individual competencies and leaders' abilities to provide benefits *or* impose costs, with these dimensions interacting with market forces rooted in follower preferences, group context, and cultural norms.  -->
 <!-- Whereas @pietraszewski_evolution_2019 emphasizes leaders ability to propose various enterprises and followers ability to evaluate them, -->

>>>>

```{r fivefold, fig.width=10, fig.cap="The intersections of evidence for our five basic elements of leadership among all text records (an 'upset' plot) [@gehlenborg2019]. Horizontal bars (left): The total number of text records in each element. Dots (bottom): Elements that both have evidence (intersection). Vertical bars (top): The number of text records in that intersection. Red: The number of text records involving shamans or leaders with supernatural qualities. "}

shamanfn <- function(row){
  row['shamanism'] == 'Shaman'
}

upset(
  df_fivefold2,
  nintersects = 18,
  order.by = 'freq',
  point.size = 5, 
  text.scale = 2,
  queries = list(list(query = shamanfn, color = 'red', active=T))
)

As Figure \@ref(fig:fivefold) reveals, descriptions of leadership in the ethnographic record includes a heterogeneous mix of these traits. In particular, not all leaders have evidence for high *Social capital*, leaders with *Cognitive capital* provide benefits *and* impose costs, and *Somatic capital* is rarely mentioned, but when it is, it is associated with providing benefits as well as imposing costs. Shamans are associated with evidence for *Cognitive capital* and imposing costs.

<!-- Leadership and followership stem from biological market forces and information-processing roles [e.g., @garfield_evolutionary_2019; @hagen_leadership_2019; @pietraszewski_evolution_2019]. Much of human leadership goes beyond group coordination problems, such as leaders important roles in devising strategic outcomes between individuals, offering advice or decision-making services to individuals, and in making direct prosocial investments that do not involve substantial coordination. We therefore suggest leadership dynamics emerge from inter-individual competencies and leaders' abilities to provide benefits *or* impose costs, with these dimensions interacting with market forces rooted in follower preferences, group context, and cultural norms.  -->

 <!-- Whereas @pietraszewski_evolution_2019 emphasizes leaders ability to propose various enterprises and followers ability to evaluate them, -->
